A possibilistic valid-time model

### 2011-11-14 ipmu2012/preliminaries.tex
In this revision, I cleaned up the list of references a little. Now it spreads over 1.5 pages approximately. It would be nice to get it on one single page...

%Introductory text:
This background section is dedicated to introduce some basic concepts about possibilistic variables, the differences between fuzzy numbers and intervals. The interval evaluation by means of ill-known constraints is explained.

The preliminaries section concludes with a brief introduction to temporal databases.

\subsection{Possibilistic Variables}
A possibilistic variable $X$ over a universe $U$ is defined as a variable taking exactly one value in $U$, but for which this value is (partially) unknown. The possibility distribution $\pi_X$ gives the available knowledge about the value that $X$ takes. For each $u\in U$, $\pi_X(u)$ represents the possibility that $X$ takes the value $u$.

@@

\subsection{Temporal databases}
%In this section, the proposed reasoning is applied to the specific context of intervals on the real line. This setting is of specific interest in the context of fuzzy temporal databases.
A temporal database \cite{Dyreson1994} is a database that manages some aspects of time in its schema. A \textbf{chronon} is the shortest duration of time supported by the database. The time can be represented either as points or intervals \cite{655777}. Fuzzy temporal models \cite{schockaert08} are proposed when the time points or intervals are not precisely known. There are proposals for the  fuzzyfication of the time point \cite{Dubois89} and the fuzzyfication of the time interval \cite{Garrido2009}.\\
Allen \cite{Allen83} studied the comparison between two crisp time intervals. For fuzzy intervals, several proposals \cite{ohlbach04,nagypal03,schockaert08} have been done.

@@

Despite of user-defined time (an uninterpreted attribute; supported in the standard SQL2 \cite{Mel93}), there are 3 types of time in a temporal database:

@@

	 The  database model can be then classified into: transaction time \cite{Ston87},\cite{Jensen91}, Valid time, bi-temporal \cite{Snodgrass84}(both valid and transaction time) or tri-temporal \cite{Nascimento95} (valid, transaction and decision time).

>>>>

%Introductory text:
In this section, some basic concepts are introduced, concerning possibility theory, possibilistic variables and fuzzy numbers and intervals. The framework of set evaluation by ill-known constraints\cite{Pon11} is explained. The section concludes with a brief introduction to temporal databases.

\subsection{\label{subsec:possibility-theory}Possibility Theory}
Possibility theory, like probability theory, deals with uncertainty about the outcome of an experiment. In probability theory, this uncertainty is caused by the variability in the outcomes, while in possibility theory, the uncertainty is caused by incomplete knowledge on the experiment.

\subsection{\label{subsec:possibilistic-variables}Possibilistic Variables}
A possibilistic variable $X$ over a universe $U$ is defined as a variable taking exactly one value in $U$, but for which this value is (partially) unknown. The possibility distribution $\pi_X$ gives the available knowledge about the value that $X$ takes. For each $u\in U$, $\pi_X(u)$ represents the possibility that $X$ takes the value $u$.

@@

\subsection{Temporal databases}
%In this section, the proposed reasoning is applied to the specific context of intervals on the real line. This setting is of specific interest in the context of fuzzy temporal databases.
A temporal database \cite{Dyreson1994} is a database that manages some aspects of time in its schema. A \textbf{chronon} is the shortest duration of time supported by the database. The time can be represented either as points or intervals \cite{655777}. Fuzzy temporal models \cite{schockaert08} are proposed when the time points or intervals are not precisely known. There are proposals for the  fuzzyfication of the time point and the fuzzyfication of the time interval.\\
Allen \cite{Allen83} studied the comparison between two crisp time intervals. For fuzzy intervals, several proposals \cite{ohlbach04,nagypal03,schockaert08} have been done.

@@

Despite of user-defined time (an uninterpreted attribute; supported in the standard SQL2), there are 3 types of time in a temporal database:

@@

	 The  database model can be then classified into: transaction time \cite{Jensen91}, Valid time, bi-temporal \cite{Snodgrass84}(both valid and transaction time) or tri-temporal \cite{Nascimento95} (valid, transaction and decision time).
